Open source landscape ecology tools

### 2020-07-18 paper/paper.Rmd
adds new ideas

@@

<!-- the role of data preparation - cropping, reprojecting, chaning resolution/simplifing, merging/joing -->

@@

>>>>

<!-- JN: maybe we can also add info about RMarkdown and similar, with R as an integrative tool for making scientific outputs -->

@@

<!-- the role of data preparation - cropping, reprojecting, changing resolution/simplifying, merging/joining -->

@@

<!-- JN: I am also thinking (unsure yet) about mentioning R as a bridge between other software (e.g. GRASSGIS) -->
